TGI-spinal-power

### 2022-05-10 analysis/tgispine_lme_power.Rmd
trying (& failing) to get the simr to work with glmm

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,])
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::betabinomial(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'warm' ,])
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
plot(model.cold.assmup)
```

@@

# extract relevant effect sizes
tgi_effect <- fixef(model.cold.ex)["manipulationTGI"]
cond_effect <- fixef(model.cold.ex)["conditionwithin"]
cold_loc_effect <- fixef(model.cold.ex)["cold_locationprox_caud"]

# power analysis - using smallest effect size
fixef(model.cold.ex)["manipulationTGI"] <- cold_loc_effect
pwr.warm <- powerSim(model.warmN)
print(pwr.warm)

>>>>

# Now to model effects! Try a zero inflated regression model
```{r}
# First model cold VAS
model.cold = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'cold' ,],
                      na.action = na.omit)
# then model warm VAS
model.warm = glmmTMB::glmmTMB(beta ~ manipulation + condition + cold_location + trial_n +
                                (1|ID),
                      family = glmmTMB::beta_family(),
                      ziformula = ~1+manipulation,
                      data = df_VAS[df_VAS$VAS == 'warm' ,])
# model summaries
summary(model.cold)
summary(model.warm)
```
# Look at model assumptions
```{r}
# cold assumption
model.cold.assmup <- simulateResiduals(model.cold, n = 1000)
plot(model.cold.assmup)
```

@@

# extract relevant effect sizes
tgi_effect <- fixef(model.cold.ex)[['cond']][['manipulationTGI']]
cond_effect <- fixef(model.cold.ex)[['cond']][['conditionwithin']]
cold_loc_effect <- fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']]

# power analysis - using smallest effect size
fixef(model.cold.ex)[['cond']][['cold_locationprox_caud']] <- .2
pwr.cold <- powerSim(model.cold.ex)
print(pwr.cold)
